Model

### 2019-11-18 stats/model.Rmd
fix model bug

  query.add(["modelPrediction","pragmatic","free", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(pragModelPredictions.score(1))])

//  query.add(["modelPrediction","globalPrag","free", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(globalPragModelPredictions.score(1))])

>>>>

  query.add(["modelPrediction","pragmatic","free", row.alignment, row.item, row.subid], [row.age, Math.exp(pragModelPredictions.score(1))])

//  query.add(["modelPrediction","globalPrag","free", row.alignment, row.item, row.subid], [row.age, Math.exp(globalPragModelPredictions.score(1))])
